Decade of Lost Precision: A General Framework For Image Feature Matching Without Geometric Constraints

### 2014-11-28 paper.tex
Corrected per suggestions

Brown and Lowe \cite{brown2005multi} extend ratio match to deal with a set of images by using not the ratio of the best and second best correspondence, but the average ratio of the best and the average of second best correspondences across a set of images.  Rabin et al.\ \cite{rabin2009statistical} try to enhance descriptor matching by looking at the statistical distribution of local features in the matched images, and only return a match when such a correspondence would not occur by mere chance. Finally, a precursor of the algorithms discussed in this paper was introduced by the authors as \emph{Mirror-Match} \cite{arnfred2013mirror}, which makes use of the feature points in both images to decide if a match is valid.

A plethora of solutions have combined ratio match with various geometric constraints to improve matching. These constraints are based on assumptions regarding the transformation between the query and \emph{target images}. At the stricter end we have epipolar constraints, assuming that the images can be tied by a homography \cite{torr2000mlesac, chum2005matching}, and angular constraints, assuming the correspondences are angled similarly \cite{kim2008efficient, schmid1997local}. Often these approaches are made computationally feasible by modeling feature correspondences as an instance of graph matching, where each feature is a vertex, and edge values correspond to a geometric relation between two features. Approximate graph matching algorithms can then be used to efficiently establish an isomorphism between the graph of features in two images \cite{leordeanu2005spectral, torresani2008feature, yarkony2010covering, yuan2012efficient}. Others define image regions and reject or accept correspondences based on the regions they connect \cite{cho2009feature, wu2011robust}.

@@

The \emph{Mirror-Match} variant was originally introduced by the authors in~\cite{arnfred2013mirror}, where it was shown to be superior to \emph{Ratio-Match}. %In this paper we improve on this work by establishing formal proofs for the precision of the matching algorithms, by evaluating the algorithms on a more thorough dataset and by identifying \emph{Mirror-Match} as part of a general framework.

>>>>

Brown and Lowe \cite{brown2005multi} extend ratio match to deal with a set of images by using not the ratio of the best and second best correspondence, but the average ratio of the best and the second best correspondences across a set of images.  Rabin et al.\ \cite{rabin2009statistical} try to enhance descriptor matching by looking at the statistical distribution of local features in the matched images, and only return a match when such a correspondence would not occur by mere chance. Finally, a precursor of the algorithms discussed in this paper was introduced by the authors as \emph{Mirror-Match} \cite{arnfred2013mirror}, which makes use of the feature points in both images to decide if a match is valid.

A plethora of hybrid solutions have combined descriptor matching with various geometric constraints to improve matching. These constraints are based on assumptions regarding the transformation between the query and \emph{target images}. At the stricter end we have epipolar constraints, assuming that the images can be tied by a homography \cite{torr2000mlesac, chum2005matching}, and angular constraints, assuming the correspondences are angled similarly \cite{kim2008efficient, schmid1997local}. Often these approaches are made computationally feasible by modeling feature correspondences as an instance of graph matching, where each feature is a vertex, and edge values correspond to a geometric relation between two features. Approximate graph matching algorithms can then be used to efficiently establish an isomorphism between the graph of features in two images \cite{leordeanu2005spectral, torresani2008feature, yarkony2010covering, yuan2012efficient}. Others define image regions and reject or accept correspondences based on the regions they connect \cite{cho2009feature, wu2011robust}.

@@

The algorithms \emph{Ratio-Match}, \emph{Self-Match} and \emph{Both-Match} all find the best match to a given \emph{query feature} only in the \emph{target image}. They differ by the feature set used as the \emph{baseline set}. While \emph{Ratio-Match} uses features from the \emph{target image}, \emph{Self-Match} draws the \emph{baseline set} from the \emph{query image}. Finally \emph{Both-Match} uses the conjunction of features from both images.

Each of these three algorithms has an `extended' case where the proposal set is replaced with the conjunction of features from both the \emph{target image} and the \emph{query image}. The extended version of \emph{Self-Match} is \emph{Self-Match-Ext} and the extended version of \emph{Ratio-Match} is \emph{Ratio-Match-Ext}. Finally we call the extended version of \emph{Both-Match} for \emph{Mirror-Match} because it was under this name that the algorithm was originally introduced by the authors in~\cite{arnfred2013mirror}.
